### 2024-07-07 getting-started.qmd
20240706 - clarifications

1. Install `R`: <https://cran.r-project.org>
1. Install `RStudio Desktop`: <https://posit.co/download/rstudio-desktop>
1. After installing `RStudio`, open `RStudio` and run the following code in the console to install several key `R` packages:

install.packages(
  c("petersenlab","ffanalytics","nflreadr","nflfastR","nfl4th","nflplotR",
  "gsisdecoder","progressr","lubridate","tidyverse","psych"))
```

@@

For instance, to learn about the `seq()` function, which creates a sequence of numbers, you can execute the following command:

@@

@@

The `seq()` function takes the following arguments:

@@

You can specify a function and its arguments either by providing values for each argument in the order indicated by the function, or by naming its arguments.

Here is an example of providing values to the arguments in the order indicated by the function:

@@

If you want to generate a series with gradually incrementing decimal places, you could specify a long desired sequence of 81 values:

@@

@@

>>>>

1. Install `R`: <https://cran.r-project.org>
1. Install `RStudio Desktop`: <https://posit.co/download/rstudio-desktop>
1. After installing `RStudio`, open `RStudio` and run the following code in the console to install several key `R` packages:
```{r}
#| eval: false

install.packages(
  c("petersenlab","remotes","nflreadr","nflfastR","nfl4th","nflplotR",
  "gsisdecoder","progressr","lubridate","tidyverse","psych"))
```
1. Some necessary packages, including the `ffanalytics` package, are hosted in GitHub and need to be installed using the following code (after installing the `remotes` package above):
```{r}
#| eval: false

remotes::install_github("FantasyFootballAnalytics/ffanalytics")
```

@@

Below, we provide examples for how to learn about and use functions and arguments, by using the `seq()` function as an example.
The `seq()` function creates a sequence of numbers.
To learn about the `seq()` function, which creates a sequence of numbers, you can execute the following command:

@@

This is what the documentation shows for the `seq()` function in the `Usage` section:

@@

Based on this information, we know that the `seq()` function takes the following arguments:

@@

What each argument represents (i.e., the meaning of `from`, `to`, `by`, etc.) is provided in the `Arguments` section of the documentation.
You can specify a function and its arguments either by providing values for each argument in the order indicated by the function, or by naming its arguments.

Here is an example of providing values to the arguments in the order indicated by the function, to create a sequence of numbers from 1 to 9:

@@

If you want to generate a series with decimal values, you could specify a long desired sequence of 81 values:

@@

Hopefully, that provides an example for how to learn about a particular function, its arguments, and how to use them.

@@

Below, we provide examples for how to download various types of football data.
